\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2019-01-02 archive.tex
improvements to dreaming part of big figure

    \begin{scope}[shift={(9.5,-4.5)}]
      \node(dreaming) at (2,-1) {\underline{Fantasies}};
      \node at ([yshift=-0.75cm,xshift=-1.5cm]dreaming.south) (d){DSL};
      \node at ([xshift=1.5cm]d.east) (p1){prog.};
      \draw[squiggle,-> ] (d.east) -- node[sloped,above]{\small sample} (p1.west);
      \node at ([xshift = 1.5cm]p1.east) (t1){ task};
      \draw [-> ] (p1.east) -- node[above]{\small run} (t1.west);
      \node(n) at ([yshift=-1.2cm,xshift=0.4cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [dashed] (p1.south) to[out=-120,in=180] node[above,fill=white]{\color{black}Loss} ([xshift=-0.4cm]n.west);

      \node(replay) at (2,-5) {\underline{Replays}};
      \node[align=center] at ([yshift=-0.75cm,xshift=-1.5cm]replay.south) (d){progs.\\for\\task};
      \node at ([xshift=1.5cm]d.east) (p1){prog.};
      \draw[squiggle,-> ] (d.east) -- node[sloped,above]{\small sample} (p1.west);
      \node at ([xshift = 1.5cm]p1.east) (t1){ task};
      \draw [-> ] (p1.east) -- node[above]{\small run} (t1.west);
      \node(n) at ([yshift=-1.2cm,xshift=0.4cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [dashed] (p1.south) to[out=-120,in=180] node[above,fill=white]{\color{black}Loss} ([xshift=-0.4cm]n.west);

>>>>

    \begin{scope}[shift={(9.5,-4.5)}]
      \node(dreaming) at (1,-1) {\underline{Fantasies}};
      \node[anchor=center] at ([yshift=-0.5cm]dreaming.south) (d){\textbf{DSL}};
      \node at ([yshift=-1.75cm]d.south) (p1){program};
      \draw[squiggle,-> ] (d.south) -- node[sloped,above]{\small sample} (p1.north);

      \node(replay) at ([xshift=2cm]dreaming.east) {\underline{Replays}};
      \node[anchor=center,align=center] at ([yshift=-0.5cm]replay.south) (d){\textbf{progs. for task}};
      \node at ([yshift=-1.75cm]d.south) (p1){program};
      \draw[squiggle,-> ] (d.south) -- node[sloped,above]{\small sample} (p1.north);

      \node(p1) at (1.5,-6) {program};      
      \node at ([xshift = 2.0cm]p1.east) (t1){ task};
      \draw [-> ] (p1.east) -- node[above]{\small run} (t1.west);
      \node(n) at ([yshift=-1.2cm,xshift=0.4cm]p1.south) {
        \NeuralNetwork{0.17}};
      \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      \draw [dashed] (p1.south) to[out=-120,in=180] node[above,fill=white]{\color{black}Loss} ([xshift=-0.4cm]n.west);

      \node at ($(-0.25,0.5) + (p1.north)!0.5!(t1.north)$) {\underline{Train recognition model}};

      %% \node at ([xshift = 1.5cm]p1.east) (t1){ task};
      %% \draw [-> ] (p1.east) -- node[above]{\small run} (t1.west);
      %% \node(n) at ([yshift=-1.2cm,xshift=0.4cm]p1.south) {
      %%   \NeuralNetwork{0.17}};
      %% \draw [->,red] (t1.south) to[out = -90,in = 0]  ([xshift=0.4cm]n.east);
      %% \draw [dashed] (p1.south) to[out=-120,in=180] node[above,fill=white]{\color{black}Loss} ([xshift=-0.4cm]n.west);
